---
title: "README"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Simple R Package to query the NYTimes article search API. 

Note: The `rtimes` packages was abandoned, and it seemed easier to write a simple package to only query the AS API rather than 
taking over the whole package.

## Installation

```{r, eval=F}
remotes::install_github("vanatteveldt/nytimes")
```

## API Key

To get an API key, visit https://developer.nytimes.com/get-started.
The first time you use this package, it will prompt you for the key and store it.
You can also store it manually using:

```{r, eval=F}
options(NYTIMES_API_KEY="<YOUR API KEY>")
```

## Using the API

The main function to use is the `query` function. 
Apart from an optional API_KEY and max_pages argument, this passes all arguments directly to the article search API.
For example, to get the first 20 front page articles of 2020 election news, you could use something like:

```{r}
library(nytimes)
query(fq='(biden OR trump) AND source:"The New York Times" AND print_section:A AND print_page:1', begin_date="2020-01-01", end_date="2020-11-03",
      max_pages=2)
```
